### 2016-05-09 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More edits

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.82,0.88),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.background = element_rect(fill = grey(0.9))) +
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 0,y = 1.8,label = 'A')

@@

#First calculate Delta RTL 
temp <- subset(dd,!duplicated(paste0(BirdID,Agemonths)))
counts <- with(temp,tapply(RTL,BirdID,length))
c3 <- names(counts[counts >= 2])

dd3 <- subset(temp,BirdID %in% c3)

ggplot(dd3,aes(x = Agemonths,y = RTL, group = BirdID))+
  geom_line(alpha = 0.5)

dd3$DeltaRTL <- NA

@@

temp <- subset(dd3,DeltaRTL != 0)

boxplot(DeltaRTL~SurvivedNext,data=subset(temp,MinAge>1))
summary(lm(DeltaRTL~RemainingLife,data=subset(temp,MinAge>1)))

plot(DeltaRTL~LayYear,data=subset(temp,MinAge>1 ))

temp <- subset(dd0,!duplicated(paste0(BloodID,RTL)))

temp <- subset(temp,RTL<2)
temp <- subset(temp,RTL > 0.04)

@@

dd3 <- subset(dd3,DeltaRTL !=0)
dd3_2 <- subset(dd3_2,DeltaRTL!=0)

dd3_2 <- dd3_2[1:nrow(dd3),]

@@

Fig4C <- ggplot(temp,aes(col=Group,fill = Group,x = DeltaRTL, y = ..scaled..))+
    geom_density(alpha = 0.2)+
  theme_classic()+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.22,0.78),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)+
  annotate('text',x = -5,y = 2,label = 'C')

@@

#First calculate Delta RTL 
temp <- subset(dd,!duplicated(paste0(BirdID,Agemonths)))
counts <- with(temp,tapply(RTL,BirdID,length))
c3 <- names(counts[counts >= 2])

dd3 <- subset(temp,BirdID %in% c3)

ggplot(dd3,aes(x = Agemonths,y = RTL, group = BirdID))+
  geom_line(alpha = 0.5)

dd3$DeltaRTL <- NA

temp <- subset(dd3,DeltaRTL != 0)

boxplot(DeltaRTL~SurvivedNext,data=subset(temp,MinAge>1))
summary(lm(DeltaRTL~RemainingLife,data=subset(temp,MinAge>1)))

plot(DeltaRTL~LayYear,data=subset(temp,MinAge>1 ))

temp <- subset(dd0,!duplicated(paste0(BloodID,RTL)))

temp <- subset(temp,RTL<2)
temp <- subset(temp,RTL > 0.04)

dd3 <- subset(dd3,DeltaRTL !=0)
dd3_2 <- subset(dd3_2,DeltaRTL!=0)

dd3_2 <- dd3_2[1:nrow(dd3),]

ggplot(temp,aes(col=Group,fill = Group,x = DeltaRTL))+
    geom_histogram()+
  theme_classic()+
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)

>>>>

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.82,0.88),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.background = element_rect(fill = grey(0.9))) +
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 0,y = 1.8,label = 'A')

@@

#First calculate Delta RTL 
temp <- subset(dd,!duplicated(paste0(BirdID,Agemonths)))
counts <- with(temp,tapply(RTL,BirdID,length))
c3 <- names(counts[counts >= 2])
dd3 <- subset(temp,BirdID %in% c3)
DeltaRTL <- NA

@@

temp <- subset(dd0,!duplicated(paste0(BloodID,RTL)))
temp <- subset(temp,RTL<2)
temp <- subset(temp,RTL > 0.04)

@@

dd3 <- subset(dd3,DeltaRTL !=0)
dd3_2 <- subset(dd3_2,DeltaRTL!=0)
dd3_2 <- dd3_2[1:nrow(dd3),]

@@

Fig4C <- ggplot(temp,aes(col=Group,fill = Group,x = DeltaRTL, y = ..scaled..))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c(0.22,0.78),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)+
  annotate('text',x = -2,y = 1,label = 'C')

@@
